\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix-2020-09}

% to be able to draw some self-contained figs
\usepackage{tikz}
\usepackage{amsmath}

% inlined bib file
\usepackage{filecontents}

%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

%don't want date printed
\date{}

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Implementing a Secure Microservice Architecture:\\
  NGINX \& Kubernetes Deployment}

%for single author (just remove % characters)
\author{
{\rm Orchestration: Alexander Moomaw}\\
Eastern Washington University
\and
{\rm Services: Andre Ramirez}\\
Eastern Washington University
\and
{\rm Logging: Brendan Hopkins}\\
Eastern Washington University
\and
{\rm Services: Beighlor Martinez}\\
Eastern Washington University
\and
{\rm Defense: Cameron Olivier}\\
Eastern Washington University
\and
{\rm Frontend: Dillon Pikulik}\\
Eastern Washington University
\and
{\rm Project Management: Chelsea Edwards}\\
Eastern Washington University
}
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
 % end author

\maketitle
%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
This paper presents a secure and scalable deployment architecture for web server environments using Kubernetes. 
The deployment incorporates a proxy and web application firewall for enhanced security and modular design. 
Additionally, we introduce our solution to logging and IP banning mechanisms to monitor and restrict unauthorized access. 
Our approach ensures high availability, load balancing, and robust defense against threats, offering a comprehensive framework for modern web applications.
\end{abstract}

%-------------------------------------------------------------------------------
\section{Introduction}
%-------------------------------------------------------------------------------
\input{intro}

%-------------------------------------------------------------------------------
\section{Orchestration}
%-------------------------------------------------------------------------------
\input{orchestration}

%-------------------------------------------------------------------------------
\section{Floating Figures and Lists}

\input{systemDes}
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
\section{Logging and IP Gathering}
To enhance the security of our web server environment, we implemented a robust mechanism 
for gathering and logging IP addresses. This approach involves capturing IP addresses 
attempting to access our server on ports other than 22 (SSH) and 80 (HTTP) and maintaining 
comprehensive logs for further analysis. 
The IP gathering mechanism is designed to identify unauthorized access attempts by capturing IP
addresses that try to connect to non-standard ports. This is achieved through a script that utilizes
tcpdump to monitor network traffic and filter out unwanted connections. The captured IP addresses 
are stored in a cumulative list, which can be used to block malicious IPs via IP tables.
In addition to gathering IP addresses, we implemented an hourly logging mechanism to maintain detailed
records of network activity. This involves running a script that logs all IP traffic, excluding ports 22 and 80,
and saves the logs with timestamps. These logs provide valuable data for analyzing traffic patterns and identifying 
potential security threats.
To ensure the effectiveness of our IP gathering and logging mechanisms, the captured IP addresses and logs are periodically 
reviewed. This verification process involves accessing the log files to confirm that the security measures are functioning as 
intended and to identify any anomalies in network traffic.
\input{threatMod}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\section{Floating Figures and Lists}

\input{eval}
%-------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{refs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%  LocalWords:  endnotes includegraphics fread ptr nobj noindent
%%  LocalWords:  pdflatex acks
